### 2019-02-20 review/referee_response_0.txt

ii) Similar to Figure 3, I would recommend changing the title indicated in bold
font in Figure 6, by a more explicit sentence about what is shown in the plot.
For eample "Different apsidal precession and orbital decay models for the O-C
values" or something like that.

  > Response: As in Figure 3, we appreciate the suggestion, but have opted to
  > keep the "title" as is. We have appended the sentence "The two models may
  > begin to diverge in the mid-2020s" as further clarification for the reader.

iii) Mb is indicated as the mass of the hypothetical planet WASP-4c, however,
the Mb symbol is not present in equation (19).

  > Response: We have correcly the wording accordingly.

iv) Why do the authors assume k2b = 0.6 for the Love number? Is this value
randomly chosen?

  > Response: We have added the phrase "similar to Jupiter". Section 4.2
  > already notes that our measured value for k_2p under the precession
  > hypothesis (Equation 18) is imprecise.

v) Would it be possible to introduce a definition of the reduced mass presented
in equation 21? Also, could the authors specify which values they used for L,
Mc, and Rc and provide references?

  > Response: We have clarified the origin of the values used when evaluating
  > Equation 21.  The tricky ones -- the mass and radius of the convective
  > envelope -- came from the MESA/MIST projects, for which we have added
  > appropriate citations.  Our thanks to the referee for pointing out this
  > omission.  We have opted to not explicitly define the reduced mass, as it
  > is standard knowledge in the gravitational two-body problem.

********************************************************************************

Referee comment:

i) "WASP-4 timing anomaly" --> "WASP-4b timing anomaly"

  > Response: Corrected.

ii) In the caption of Figure 7: "with standard deviation (σpredicted)" -->
"with standard deviation (σpre-TESS)"

  > Response: Corrected.
